\documentclass[overlapped,line,letterpaper]{res1}

\usepackage{ifpdf}
\usepackage{fancyhdr}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{url}
\usepackage{enumitem}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Jia Liu},
  pdfcreator={$ $Id: cv-us.tex,v 1.23 2006/06/21 00:14:55 jrblevin Exp $ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={economics microeconomics econometrics empirical urban
    game theory applied mathematics differential equations TANH method
    hyperbolic tangent centroid decomposition updating singular value
    decomposition linear algebra microeconomics linux unix german}
}

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}

\addtolength{\textheight}{-0.8cm} %\addtolength{\voffset}{-0.2in}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%%===========================================================================%%

\setlist[enumerate,1]{leftmargin=\dimexpr 26pt-.2in}

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
%\setlength{\leftmargini}{0em}
%\renewcommand{\labelitemi}{}

%% Use large bold font for printed name at top of pages
%\renewcommand{\namefont}{\large\textbf}
%
%\renewcommand{\headrulewidth}{0pt}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

\pagestyle{fancy} \headheight0pt \lfoot{\hspace{-.5in}{Updated: \today}}
 \rfoot{\bf \thepage} \cfoot{}

\renewcommand{\headrulewidth}{0pt}


%---------------------------------------------------------------------------
\name{\LARGE Jia (Kevin) Liu}

\begin{resume}

\section{\bf \large Contact Information}
\vspace{.1in}
\begin{ncolumn}{2}
    209 Atanasoff Hall       & \hspace{-.5in} E-mail: {\tt jialiu@iastate.edu}, \,\, Phone: (515) 294-2582 \\
  Ames, IA 50011, U.S.A.                      & \hspace{-.5in} Web: {\tt \verb+http://web.cs.iastate.edu/~jialiu/+} \\
\end{ncolumn}

%---------------------------------------------------------------------------

\section{\bf \large Research Interests}
\vspace{.24in}
\begin{list2}
%\item Internet-of-Things, Autonomous Systems, Cyber-Physical Systems
\item Optimization for Machine Learning, Distributed Learning
\item Reinforcement Learning, Multi-Armed Bandits
\item Generalization and Model Compression in Machine Learning
\item Stochastic Network Optimization and Control Theory
\end{list2}


%data analytics, convex and non-convex optimization,  neural networks and multi-armed bandits, and machine learning


\section{\bf \large Education}
\vspace{.1in}
{\bf Ph.D. in Electrical and Computer Engineering} \\ %, Feb. 2010 \\
{\bf Virginia Tech}, Blacksburg, VA
 %\\{\em Dissertation Topic:} ``MIMO-based Wireless Networks: Modeling and Optimization'' \\
%{\em Advisor:} Prof. Thomas Hou 
%{\em Dissertation Committee Member and Collaborator (22 papers):} Prof. Hanif Sherali
\vspace{-.02in}
%GPA: 3.97/4.00

{\bf M.S. in Electrical Engineering} \\ %, Mar. 1999 \\
{\bf South China University of Technology}, Guangzhou, Guangdong, P. R. China
\vspace{-.02in}

{\bf B.S. in Electrical Engineering and Computer Science} \\ %, Jul. 1996 \\
{\bf South China University of Technology}, Guangzhou, Guangdong, P. R. China



%---------------------------------------------------------------------------
\section{\bf \large Employment in Academia and Industry}

\vspace{.1in}
{\bf Assistant Professor}, {Dept. of Computer Science, Iowa State University, Aug. 2017 - Present} \\
\vspace{-.16in}\\
{\em Research Areas:} Internet-of-Things, Machine Learning, Cyber-Physical Systems (CPS), Data Analytics, Mobile Computing, Cloud Computing, Software-Defined Networks, Network Economy \\
\vspace{-.22in}

\vspace{.1in}
{\bf Research Assistant Professor}, {Dept. of Electrical and Computer Engineering, The Ohio State University, Nov. 2014 - Jul. 2017} \\
\vspace{-.16in}\\
{\em Research Areas:} Internet-of-Things (IoT), Cyber-Physical Systems (CPS), Data Analytics Infrastructure, Mobile Computing, Cloud Computing, Software-Defined Networks, Network Economy \\
\vspace{-.22in}

{\bf Postdoctoral Researcher}, {Dept. of ECE, The Ohio State University, Apr. 2010 - Oct. 2014} \\
\vspace{-.16in}\\
{\em Research Areas:} Wireless Networks, Cloud Computing, Data Analytics, Smart Grid\\ 
\smallskip
{\em Advisor:} Prof. Ness B. Shroff \\
\vspace{-.22in}


%{\bf Graduate Research Assistant}, {Virginia Tech, September 2003 - February 2010} \\
%\vspace{-.16in}\\
%{\em Advisor:} Prof. Y. Thomas Hou \\
%\vspace{-.2in}

%{\bf Software Engineer Summer Intern}, {Mercury Computer Systems, Inc., Chelmsford, MA, June 2005 - August 2005} \\
%{\em Project:} Developed Linux drivers for Rapid IO$^\circledR$ bus (used in Mercury's cognitive radio communications systems) \\
%\vspace{-.2in}
%

{\bf Member of Technical Staff}, {Bell Labs, Lucent Technologies, Mar. 1999 - Jan. 2003} \\
\medskip
{\em Responsibility:} Development of cdma2000-1x/1xEV-DO/1xEV-DV standards in China 
\vspace{-.1in}


\section{\bf \large Research Grants}
\vspace{.12in}
\hspace{-.55in} {\bf Current (Total: $\sim$ \$3.30M, Personal Share: $\sim$ \$2.20M):}

\hspace{-.55in} {\em A) National Science Foundation (NSF)}
\vspace*{.08in}

\begin{enumerate}
\vspace*{.08in} \item {\bf NSF CNS-1943226}, ``CAREER: Computing-Aware Network Optimization for Efficient Distributed Data Analytics at the Wireless Edge,'' \$524,125 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf NSF ECCS-1731649}, ``SpecEES: Toward Spectral and Energy Efficient Cross-Layer Designs for Millimeter-Wave-Based Massive MIMO Networks,'' National Science Foundation (NSF), \$549,999, 08/15/2017 -- 07/31/2020 ({\bf Lead PI}, Co-PI: John Volakis).

\vspace*{.08in} \item {\bf NSF CCF-1618318}, ``CIF: Small: Taming Convergence and Delay in Stochastic Network Optimization with Hessian Information,'' National Science Foundation (NSF), \$317,896, 07/01/2016 -- 06/30/2019, extended to 6/30/2020 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf NSF CNS-1527078}, ``NeTS: Small: Toward Optimal, Efficient, and Holistic Networking Design for Massive-MIMO Wireless Networks,'' National Science Foundation (NSF), \$300,000, 10/01/2015 -- 09/30/2018, extended to 09/30/2020 ({\bf Sole PI}).

\vspace*{.08in}
\hspace{-.55in}  {\em B) Department of Defense (DoD) Funding Agencies}

\vspace*{.08in} \item {\bf AFRL FA8750-18-1-0107}, ``Taming Delay and Convergence Speed in Tactical Autonomous Swarms Network Optimization,'' Air Force Research Laboratory (AFRL), \$500,000, 07/10/2018 -- 01/01/2021 ({\bf Sole PI}).


\vspace*{.08in} \item {\bf ONR N000014-17-1-2417}, ``Achieving Low Delay and Highly Adaptive Tactical Networking with Multi-Path TCP,'' Office of Naval Research (ONR), \$1,050,000 ({\bf ONR 6.2}, {\bf Co-PI}, my share: \$200,000, PI: Ness B. Shroff, 06/2017 -- 05/2020).

\vspace*{.08in} \item {\bf AFRL 2020 Visiting Faculty Research Program (VFRP) Award}, ``Communication-Efficient Distributed Data Analytics over Tactical UAV Swarms,''  \$15,000, 05/18/2020 -- 07/10/2019 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2019 Visiting Faculty Research Program (VFRP) Award}, ``Optimal Energy Control for Autonomous Solar-Powered Long-Cruising Tactical UAV Swarms,''  \$15,000, 06/10/2019 -- 08/02/2019 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2019 Summer Extension Grant}, ``Optimal Energy Control for Autonomous Solar-Powered Long-Cruising Tactical UAV Swarms,''  \$10,000, 08/02/2019 -- 11/14/2019 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2018 Summer Extension Grant}, ``Taming Delay, Convergence Speed, and Energy Efficiency for AirborneWireless Networks,''  \$10,000, 08/29/2018 -- 10/31/2018 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2018 Visiting Faculty Research Program (VFRP) Award}, ``Efficient and Elastic Tactical Resource Allocation Optimization for Airborne Autonomous Swarms,''  \$15,000, 07/02/2018 -- 08/24/2018 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2017 Research Grant}, ``Momentum-Based Dynamic Resource Allocation for Unmanned Airborne
Wireless Network Optimization,''  \$10,000, 08/29/2017 -- 10/31/2017 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFOSR 2016 Summer Faculty Fellowship Program (SFFP) Award}, ``Toward Optimal, Efficient, and Adaptive Resource Allocation Designs for Airborne Wireless Networks,'' \$32,610, 05/23/2016 -- 08/12/2016 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFOSR 2016 Summer Faculty Fellowship Program (SFFP) Extension Grant}, ``Toward Optimal, Efficient, and Adaptive Resource Allocation Designs for Airborne Wireless Networks,''  \$40,000, 08/13/2016 -- 10/31/2016 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2015 Visiting Faculty Research Program (VFRP) Award}, ``Dynamic Resource Allocation for Airborne Networks under Spectral, Spatial, and Temporal Uncertainty,''  \$15,000, 06/22/2015 -- 08/28/2015 ({\bf Sole PI}).

\vspace*{.08in} \item {\bf AFRL 2015 Summer Extension Grant}, ``Dynamic Resource Allocation for Airborne Networks under Spectral, Spatial, and Temporal Uncertainty,''  \$10,000, 08/29/2015 -- 10/31/2015 ({\bf Sole PI}).

\vspace*{.08in}
\hspace{-.55in}  {\em C) Industrial Grants and Gifts}

\vspace*{.08in} \item {\bf Google Faculty Research Award 2020}, ``Achieving Data Freshness with Selfish Users in Large-Scale Mobile Crowd-Sourcing,'' \$33,917.

\vspace*{.08in}
\hspace{-.55in}  {\em D) Other Fundings (Senior Personnel)}

\vspace*{.08in} \item {\bf NSF-CCF-1934884}, ``HDR TRIPODS: D4 (Dependable Data-Driven Discovery) Institute,'' \$1,500,000, Oct. 2019 -- Sep. 2022 (Senior Personnel, Lead PI: Prof. Hridesh Rajan, My share: 0.2 months).

\vspace*{.08in} \item {\bf NSF-CNS-1556582}, ``CPS: Synergy: Collaborative Research: Cognitive Green Building: A Holistic Cyber-Physical Analytic Paradigm for Energy Sustainability," Jan. 2015 -- Dec. 2017 (Sinior Personnel, My share: \$200K, PI: Prof. Ness B. Shroff, Co-PIs: Qian Chen, Thomas Hou, Wenjing Lou).


\vspace*{.08in} \item {\bf NSF-ECCS-1232118}, ``ECCS: Toward Efficient and Distributed Cyber-Physical Systems Design for the Smart Electric Power Grid,'' Sept. 2012 -- Sept. 2015 (Senior Personnel, PI: Cathy H. Xia, Co-PI: Prof. Ness B. Shroff).


\end{enumerate}



%\hspace{-.55in} {\bf Pending:}
%\vspace*{.08in}
%
%\begin{enumerate}
%
%%\vspace*{.08in} \item NSF CNS-1704729, ``SaTC: CORE: Medium: Data-Driven Preventive and Tactical Defense in Honeypot-Enabled Cyber Systems,'' \$1,200,000 ({\bf Co-PI}, my share: \$300,000, PI: Cathy H. Xia).
%
%%\vspace*{.08in} \item NSF CCF-1910656, ``CIF: Small: Collaborative Research: Toward a Theoretical Foundation for Optimizing Information Freshness in Mobile Crowd-Learning,'' \$500,000 ({\bf Lead PI}, my share: \$250,000, Co-PI: Bin Li).
%
%%\vspace*{.08in} \item NSF CNS-1901283, ``CNS Core: Medium: Collaborative Research: UaaS - A Framework for Enabling UAVs as a Service for End-to-End Connectivity,'' \$949,982 ({\bf Co-PI}, my share: $\sim$\$200,000, Lead-PI: Ahmed Kamal).
%
%%\vspace*{.08in} \item ONR MURI, ``Broadening the Paradigm of Age-of-Information: Perspectives from Signal Processing, Communication, and Computing,'' \$7,500,000 ({\bf Co-PI}, my share: $\sim$\$1,250,000, Lead-PI: Jing Yang, The Pennsylvania State University).
%
%%\vspace*{.08in} \item NSF CPS-1932436, ``CPS: Medium: Collaborative Research: Energy-Efficient Solar-Powered Atmospheric Satellite Communication Networks,'' \$1,200,000 ({\bf Lead PI}, my share: \$410,000, Co-PI: Peng Wei, Ness B. Shroff).
%
%%\vspace*{.08in} \item NSF CNS-1943226, ``CAREER: Computing-Aware Network Optimization for Efficient Distributed Data Analytics at the Wireless Edge,'' \$524,125 ({\bf Sole PI, Current Status: Recommended}).
%
%\vspace*{.08in} \item NSF CNS-2003188, ``Collaborative Research: MLWiNS: Low-Latency, Energy-Efficient, and Secure Distributed Learning at the Wireless Edge,'' \$557,696 ({\bf Lead PI})
%
%\vspace*{.08in} \item NSF IIS-2008665, ``CHS: Small: Collaborative Research: Achieving Information Freshness and Accuracy with Selfish Users in Mobile Crowd-Learning,'' \$250,000 ({\bf Lead PI})
%
%\vspace*{.08in} \item DARPA Young Faculty Award, ``Taming Latency in Distributed AI Systems over Wireless Access Networks,'' \$1,000,000 ({\bf Sole PI})
%
%%\vspace*{.08in} \item Facebook Research Award, ``Low-Delay Distributed Training and Inference in Heterogeneous Data Centers,'' \$69,882 ({\bf Sole PI})
%
%
%\end{enumerate}



%---------------------------------------------------------------------------
\section{\bf \large Awards and Honors}
\vspace{.2in}
\begin{enumerate}
\vspace{.05in}
\item {\bf National Science Foundation (NSF) CAREER Award, 2020}

\vspace{.05in}
\item {\bf Google Faculty Research Award, 2020}

\vspace{.05in}
\item {\bf LAS Award for Early Achievement in Research, 2020}, the College of Liberal Arts and Sciences, Iowa State University

\vspace{.05in}
\item {\bf IEEE INFOCOM 2019 Best Paper Award}: Fengjiao Li, Jia Liu, and Bo Ji, ``Combinatorial Sleeping Bandits with Fairness Constraints,'' in {\em Proc. IEEE INFOCOM}, Paris, France, Apr. 29 - May 2, 2019 (also received an {\bf INFOCOM Best-in-Session Presentation Award}, 1400+ submissions, acceptance rate 19.7\%)

\vspace{.05in}
\item {\bf IEEE INFOCOM 2016 Best Paper Award}: Jia Liu, Atilla Eryilmaz, Ness B. Shroff, and Elizabeth S. Bentley, ``Heavy-Ball: A New Approach to Tame Delay and Convergence in Wireless Network Optimization,'' in {\em Proc. IEEE INFOCOM}, San Francisco, CA, Apr. 10-15, 2016 (1600+ submissions, acceptance rate 17\%)

\vspace{.05in}
\item {\bf IEEE INFOCOM 2013 Best Paper Runner-up Award}: Jia Liu, Cathy H. Xia, Ness B. Shroff, and Hanif D. Sherali, ``Distributed Cross-Layer Optimization in Wireless Networks: A Second-Order Approach,'' in {\em Proc. IEEE INFOCOM 2013}, Turin, Italy, Apr. 14-19, 2013 (one best paper and two runner-ups were awarded out of 1600+ submissions, acceptance rate 17\%)

\vspace{.05in}
\item {\bf IEEE INFOCOM 2011 Best Paper Runner-up Award}: Yi Shi, Jia Liu, Canming Jiang, Cunhao Gao, and Y. Thomas Hou, ``An Optimal Link Layer Model for Multi-hop MIMO Networks,'' in {\em Proc. IEEE INFOCOM 2011}, Shanghai, China, Apr. 10 - 15, 2011 (one best paper and one runner-up were awarded out of 1800+ submissions, acceptance rate 15\%)

\vspace{.05in}
\item {\bf IEEE ICC 2008 Best Paper Award}: Jia Liu, Y. Thomas Hou, and Hanif D. Sherali, ``Cross-Layer Optimization for MIMO-Based Mesh Networks with Dirty Paper Coding,'' in {\em Proc. IEEE ICC 2008}, Beijing, China, May 19 - 23, 2008

\vspace{.05in}
\item {\bf Joint Keynote Speaker, 05/2018}, joint EFC-IoT/RAWNET workshop, Shanghai, China

%\vspace{.05in}
%\item {\bf China National Award for Outstanding Ph.D. Students Abroad 2008} (300 awardees across all disciplines worldwide)

\vspace{.05in}
\item {\bf Air Force Office of Scientific and Research Summer Faculty Fellowship, 2016}

\vspace{.05in}
\item Co-recipient of {\bf Bell Labs President Gold Award}, Bell Labs, 2001

\vspace{.05in}
\item Paul E. Torgersen Research Competition Finalist, Virginia Tech, 2009
\end{enumerate}




%\hspace{-.55in} {\bf Other Grant Writing Experiences in Ph.D. and PostDoc Years:}
%\vspace*{.08in}
%
%\begin{enumerate}
%\vspace*{.08in} \item NSF CNS-1446582,  ``CPS: Synergy: Collaborative Research: Cognitive Green Building: A Holistic Cyber-Physical Analytic Paradigm for Energy Sustainability,'' \$1,000,000, 01/01/2015 -- 12/31/ 2017 (PI: Ness B. Shroff, Co-PIs: Qian Chen, Thomas Hou, Wenjing Lou).
%
%\vspace*{.08in} \item NSF ECCS-1232118, ``CCSS: Toward Efficient and Distributed Cyber-Physical Systems Design for the Smart Electric Power Grid,'' \$431,067, 09/01/2012 -- 08/31/2016 (main technical contributor, PI: Cathy H. Xia, Co-PI: Ness B. Shroff).
%
%\vspace*{.08in} \item ``Exploring Performance Limits of Multi-hop MIMO Networks via Tractable Models and Optimization,'' NSF ECCS 1102013, \$400,000, Jul. 2011 (assistant and technical contributor, PI: Thomas Hou).
%
%\vspace*{.08in} \item ``NeTS-WN: Capacity Problems for MIMO-Enabled Wireless Mesh Networks,'' NSF CNS 0721421, \$359,158, Sep. 2007 (assistant and technical contributor, PI: Thomas Hou).
%
%\vspace*{.08in} \item ``Novel Multi-hop Networking Technologies for MIMO Systems in Tactical Communication Networks,'' ONR N00014-08-0084, \$290,000, Dec. 2007 (assistant and technical contributor, PI: Thomas Hou).
%
%%\vspace*{.08in} \item ``A CPS Approach to Future Net-Zero Energy, Cognitive, and Adaptive Building,'' (tentative title), to be submitted to NSF CISE CPS Program, estimated \$2,000,000, Jan. 2012 (Co-PI, with Prof. Thomas Hou, Prof. Wenjing Lou, Prof. Scott Midkiff, and Prof. Qian Chen).
%%%({\em Note: Tom, I have been granted PI eligibility at OSU as a PostDoc. Could I be listed as a Co-PI in this proposal? (I won't claim any share of budget in this proposal)})
%%
%%\vspace*{.08in} \item ``Distributed Second-Order Approaches for Cross-Layer Optimization in Wireless Networks,'' (tentative title), to be submitted to NSF ECCS, estimated \$1,000,000, Jan. 2012 (Co-PI, with Prof. Ness Shroff and Prof. Honghui Xia).
%
%\end{enumerate}
%




%---------------------------------------------------------------------------
%\vspace{.1in}
\section{\bf \large Teaching Experience}

\vspace{.1in}
{\bf Iowa State University} \\
Fall 2017: COMS 672: {\em Advanced Topics in Computational Models of Learning -- Optimization for Machine Learning} \\ %(Teaching evaluation: 4.5/5) \\
Spring 2018: COMS 311: {\em Design and Analysis of Algorithms} \\
Fall 2018: COMS 578X: {\em Optimization for Machine Learning} \\
Spring 2019: COMS 311: {\em Design and Analysis of Algorithms} \\
Fall 2019: COMS 578X: {\em Optimization for Machine Learning} \\
\vspace{-.2in}

{\bf The Ohio State University} \\
Spring 2015: Network Optimization and Algorithms (Guest lecture) \\
Fall 2014: Introduction to Computer and Communication Networks (Guest lecture) \\
\vspace{-.2in}

{\bf Virginia Tech}\\
Spring 2005: Introduction to Telecommunication Networks (Teaching Assistant: Giving lectures, grading assignments and exams)

%------------------------------------------------------------------------------
\vspace{.1in}
\section{\bf \large Publications}
\vspace{.08in}
\hspace{-.55in} {\bf Refereed Journal Articles}

\begin{enumerate}
\vspace*{.08in} \item Kuangyu Zheng, Xiaorui Wang, and {\bf Jia Liu}, ``Distributed Traffic Flow Consolidation for Power Efficiency of Large-Scale Data Center Networks,'' {\em IEEE Transactions on Cloud Computing}, accepted, to appear.

\vspace*{.08in} \item Fengjiao Li, {\bf Jia Liu}, and Bo Ji, ``Combinatorial Sleeping Bandits with Fairness Constraints,'' {\em IEEE Transactions on Network Science and Engineering}, accepted, to appear.

\vspace*{.08in} \item Bin Li, {\bf Jia Liu}, and Bo Ji, ``Low-Overhead Wireless Uplink Scheduling for Large-Scale Internet-of-Things,'' {\em IEEE Transactions on Mobile Computing}, accepted, to appear.

\vspace*{.08in} \item {\bf Jia Liu} and Elizabeth S. Bentley, ``Hybrid-Beamforming-Based Millimeter-Wave Cellular Network Optimization,'' {\em IEEE Journal on Selected Areas in Communications (JSAC)}, accepted, to appear.

\vspace*{.08in} \item Hongsen Shi$^{*}$, \textbf{Jia Liu}$^{*}$, and Qian Chen, ``An RC-Network Approach for HVAC Precooling Optimization in Green Buildings,'' {\em IEEE Transactions on Sustainable Computing} ($^{*}$Co-primary authors, accepted with minor revision, fast-tracked from ACM e-Energy'18).

\vspace*{.08in} \item \textbf{Jia Liu} and Elizabeth S. Bentley, ``Hybrid-Beamforming-Based Millimeter-Wave Cellular Network Optimization,'' {\em Special Issue on Millimeter-Wave Networking, IEEE Journal on Selected Areas in Communications} (JSAC) (Accepted with revision).

\vspace*{.08in} \item Bin Li, \textbf{Jia Liu}, and Bo Ji, ``Low-Overhead Wireless Uplink Scheduling for Large-Scale Internet-of-Things,'' {\em IEEE Transactions on Mobile Computing}, (under second-round review, minor revisions).

\vspace*{.08in} \item \textbf{Jia Liu}, Atilla Eryilmaz, Ness B. Shroff, and Elizabeth S. Bentley, ``Understanding the Impacts of Limited Channel State Information on Massive MIMO Cellular Network Optimization,'' {\em IEEE Journal on Selected Areas in Communications} (JSAC), vol.~35, no.~8, pp.~1715-1727, Aug. 2017.

\vspace {.08in} \item \textbf{Jia Liu}, Ness B. Shroff, Cathy H. Xia, and Hanif D. Sherali, ``Joint Congestion Control and Routing Optimization: An Efficient Second-Order Distributed Approach,'' {\em IEEE/ACM Transaction on Networking}, vol.~24, no.~3, pp.1404-1420, Jun. 2016.

\vspace {.08in} \item \textbf{Jia Liu}, Tianyou Kou, Qian Chen, and Hanif D. Sherali, ``On Wireless Network Infrastructure Optimization for Cyber-Physical Systems in Future Smart Buildings,'' {\em International Journal on Sensor Networks}, special issue on Internet of Things (IoT), vol.~18, no.~3-4, pp.~148-160, 2015.

\vspace {.08in} \item Yi Shi, \textbf{Jia Liu}, Canming Jiang, Cunhao Gao, and Y. Thomas Hou, ``A DoF-Based Link Layer Model for Multi-Hop MIMO Networks,'' {\em IEEE Transactions on Mobile Computing}, vol.~13, no.~7, pp.~1395-1408, Jul. 2014.

\vspace{.08in} \item \textbf{Jia Liu}, Cathy H. Xia, Ness B. Shroff, and Xiaodong Zhang, ``On Distributed Computation Rate Optimization for Deploying Cloud Computing Programming Frameworks,'' {\em ACM SIGMETRICS Performance Evaluation Review} (PER), vol.~40, no.~4, pp.~63-72, Mar. 2013.

\vspace{.08in} \item Yi Shi, Y. Thomas Hou, \textbf{Jia Liu}, and Sastry Kompella, ``Bridging the Gap between Protocol and Physical Models for Wireless Networks,'' {\em IEEE Transactions on Mobile Computing}, vol.~12, no.~7, pp.~1404-1416, Jul. 2013.

\vspace {.08in} \item \textbf{Jia Liu}, Ness B. Shroff, and Hanif D. Sherali, ``Optimal Power Allocation in Multi-Relay MIMO Cooperative Networks: Theory and Algorithms,'' {\em IEEE Journal on Selected Areas in Communications} (JSAC), vol.~30, no.~2, pp.~331-340, Feb. 2012.

\vspace {.08in} \item \textbf{Jia Liu}, Tianyou Kou, Qian Chen, and Hanif D. Sherali, ``Femtocell Base Station Placement in Commercial Buildings: A Global Optimization Approach,'' {\em IEEE Journal on Selected Areas in Communications} (JSAC), vol.~30, no.~3, pp.~652-663, Apr. 2012.

\vspace {.08in} \item Sushant Sharma, Yi Shi, \textbf{Jia Liu}, Y. Thomas Hou, and Sastry Kompella, ``Network Coding in Cooperative Communications: Friend or Foe?'' {\em IEEE Transactions on Mobile Computing}, vol.~11, no.~7, pp.~1073-1085, Jul. 2012.

\vspace {.08in} \item Hui Li, Lingying Zhao, Peter Ling, and \textbf{Jia Liu}, ``A Model for Predicting Wireless Signal Transmission Performance of ZigBee-Based Sensor Networks in Residential Houses,'' {\em ASHRAE Transactions}, vol. 118, no. 1, pp. 994-1007, Jan. 2012.


\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, Yi Shi, and Hanif D. Sherali, ``Cross-Layer Optimization on Routing and Power Control of MIMO Ad Hoc Networks: Routing, Power Allocation, and Bandwidth Allocation,'' {\em IEEE Journal on Selected Areas in Communications} (JSAC), vol. 26, no. 6, pp. 913-926, Aug. 2008.

\vspace {.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, Yi Shi, and Hanif D. Sherali, ``On the Capacity of Multiuser MIMO Networks with Interference,'' {\em IEEE Transaction on Wireless Communications}, vol. 7, no. 2, pp. 488 - 494, Feb. 2008.

%\vspace {.08in} \item \textbf{Jia Liu}, Qian Chen, and Hanif D. Sherali, ``Algorithm Design for In-door Wireless Network Infrastructure,'' submitted to {\em IEEE Transaction on Mobile Computing}.

\vspace {.08in} \item \textbf{Jia Liu}, Ness B. Shroff, and Hanif D. Sherali, ``Second-Order Distributed Cross-Layer Optimization, Part I: Wireline Networks,'' submitted to {\em IEEE/ACM Transaction on Networking}.

\vspace {.08in} \item \textbf{Jia Liu}, Ness B. Shroff, and Hanif D. Sherali, ``Second-Order Distributed Cross-Layer Optimization, Part II: Wireless Networks,'' submitted to {\em IEEE/ACM Transaction on Networking}.

\vspace {.08in} \item \textbf{Jia Liu}, Cathy H. Xia, Ness B. Shroff, ``Distributed Optimal Load Shedding for Disaster Recovery in Smart Electric Power Grids,'' submitted to {\em IEEE Transactions on Smart Grid}.

\vspace {.08in} \item Kuangyu Zheng, Xiaorui Wang, and \textbf{Jia Liu}, ``Distributed Traffic Flow Consolidation for Power Efficiency of Large-Scale Data Center Network,'' submitted to {\em IEEE Transactions on Parallel and Distributed Systems}.


\end{enumerate}

%---Conference Papers---
\hspace{-.6in} {\bf Refereed Conference Papers}
\begin{enumerate}

\vspace*{.08in} \item Wenbo Ren, {\bf Jia Liu}, and Ness B. Shroff, ``The Sample Complexity of Best-$k$ Items Selection from Pairwise Comparisons,'' in {\em Proc. ICML}, Vienna, Austria, July 2020 (acceptance rate: 21.8\%).

\vspace*{.08in} \item Haibo Yang, Xin Zhang, Minghong Fang, and {\bf Jia Liu}, ``Adaptive Multi-Hierarchical signSGD for Communication-Efficient Distributed Optimization,'' in {\em Proc. IEEE SPAWC, Special Session on Distributed Signal Processing for Coding and Communications}, Atlanta, GA, May 2020 ({\bf Invited Paper}).

\vspace*{.08in} \item Ye Tian, {\bf Jia Liu}, and Cathy Xia, ``MATE: A Memory-Augmented Time-Expansion Approach for Optimal Trip-Vehicle Matching and Routing in Ride-Sharing,'' in {\em Proc. ACM e-Energy}, Melbourne, Jun. 2020 (acceptance rate: 23\%).

\vspace*{.08in} \item Xin Zhang, Minghong Fang, {\bf Jia Liu}, and Zhengyuan Zhu, ``Private and Communication-Efficient Edge Learning: A Sparse Differential Gaussian-Masking Distributed SGD Approach,'' in {\em Proc. ACM MobiHoc}, Shanghai, China, Oct. 2020 (acceptance rate: 15\%).

\vspace*{.08in} \item Zhengxiong Yuan, Bin Li, and {\bf Jia Liu}, ``Can We Improve Information Freshness with Predictions in Mobile Crowd-Learning?'' in {\em Proc. the 3rd Age of Information Workshop, IEEE INFOCOM}, Toronto, Canada, Jul. 2020.

\vspace*{.08in} \item Minghong Fang and {\bf Jia Liu}, ``Toward Low-Cost and Stable Blockchain Networks,'' in {\em Proc. IEEE ICC}, Dublin, Ireland, Jun. 2020.

\vspace*{.08in} \item Minghong Fang, Neil Zhenqiang Gong, and {\bf Jia Liu}, ``Influence Function Based Data Poisoning Attacks to Top-$N$ Recommender Systems,'' in {\em Proc. ACM WWW}, Taipei, Taiwan, Apr. 2020 (acceptance rate: 25\%).

\vspace*{.08in} \item Xuxi Yang, Lisen Deng, {\bf Jia Liu}, Peng Wei, Husheng Li, ``Multi-Agent Autonomous Operations in Urban Air Mobility with Communication Constraints,'' in {\em Proc. AIAA SciTech}, Orlando, Florida, Jan. 2020.

\vspace*{.08in} \item Xin Zhang, {\bf Jia Liu}, Zhengyuan Zhu, and Elizabeth Bentley, ``Communication-Efficient Network-Distributed Optimization with Differential-Coded Compressors,'' in {\em Proc. IEEE INFOCOM}, Toronto, Canada, Jul. 2020 (acceptance rate: 19.8\%).

\vspace*{.08in} \item Zhida Qin, Xiaoying Gan, {\bf Jia Liu}, Hongqiu Wu, Haimin Jin, and Luoyi Fu, ``Exploring Best Arm with Top Reward-Cost Ratio in Stochastic Bandits,'' in {\em Proc. IEEE INFOCOM}, Toronto, Canada, Jul. 2020 (acceptance rate: 19.8\%).

\vspace*{.08in} \item Wenbo Ren, {\bf Jia Liu}, and Ness B. Shroff, ``On Sample Complexity Upper and Lower Bounds for Exact Ranking from Noisy Comparisons,'' in {\em Proc. NeurIPS}, Vancouver, Canada, Dec. 2019 (acceptance rate: 21\%).

\vspace*{.08in} \item Haibo Yang, Xin Zhang, Minghong Fang, and \textbf{Jia Liu}$^*$, ``Byzantine-Resilient Stochastic Gradient Descent for Distributed Learning: A Lipschitz-Inspired Coordinate-wise Median Approach,'' in {\em Proc. IEEE CDC}, Nice, France, Dec. 2019.

\vspace*{.08in} \item Bin Li and \textbf{Jia Liu}$^*$, ``Can We Achieve Fresh Information with Selfish Users in Mobile Crowd-Learning?'' in {\em Proc. IEEE/IFIP WiOpt}, Avignon, France, Jun. 2019 (*Co-primary authors, acceptance rate: 42\%).

\vspace*{.08in} \item Xin Zhang, \textbf{Jia Liu}, Zhengyuan Zhu, and Elizabeth Bentley, ``Compressed Distributed Gradient Descent: Communication-Efficient Consensus over Networks,'' in {\em Proc. IEEE INFOCOM}, Paris, France, Apr. 2019 (acceptance rate: 19.7\%).

\vspace*{.08in} \item Fengjiao Li, Bo Ji, and \textbf{Jia Liu}, ``Combinatorial Sleeping Bandits with Fairness Constraints,'' in {\em Proc. IEEE INFOCOM}, Paris, France, Apr. 2019 (acceptance rate: 19.7\%).

\vspace*{.08in} \item Wenbo Ren, \textbf{Jia Liu}, Ness B. Shroff, ``Exploring $k$ out of Top $\rho$ Fraction of Arms in Stochastic Bandits,'' in {\em Proc. AISTATS}, Naha, Okinawa, Japan, Apr. 2019 (acceptance rate: 31.7\%).

\vspace*{.08in} \item Minghong Fang, Guolei Yang, Neil Zhenqiang Gong, and \textbf{Jia Liu}, ``Poisoning Attacks to Graph-Based Recommender Systems,'' in {\em Proc. ACM ACSAC}, San Juan, Puerto Rico, Dec. 2018 (acceptance rate: 20.1\%).

\vspace*{.08in} \item Hongsen Shi, \textbf{Jia Liu}, and Qian Chen, ``HVAC Precooling Optimization for Green Buildings: An RC-Network Approach,'' in {\em Proc. ACM e-Energy}, Karlsruhe, Germany, Jun. 2018 (acceptance rate: 21.9\%).

\vspace*{.08in} \item Bin Li, Bo Ji, and \textbf{Jia Liu}, ``Efficient and Low-Overhead Uplink Scheduling for Large-Scale Wireless Internet-of-Things,'' in {\em Proc. IEEE WiOpt}, Shanghai, China, May 2018 (acceptance rate: 30\%).

\vspace*{.08in} \item \textbf{Jia Liu}, ``High-Order Momentum: Improving Latency and Convergence for Wireless Network Optimization,'' in {\em Proc. IEEE INFOCOM}, Honolulu, HI, Apr. 15-19, 2018 (acceptance rate: 19\%).

\vspace*{.08in} \item \textbf{Jia Liu} and Elizabeth S. Bentley, ``Hybrid-Beamforming-Based Millimeter-Wave Cellular Network Optimization,'' in {\em Proc. IEEE WiOpt}, Paris, France, May. 15-19, 2017 (acceptance rate: 33\%).

\vspace*{.08in} \item Kuangyu Zheng, Xiaorui Wang, and \textbf{Jia Liu}, ``DISCO: Distributed Traffic Flow Consolidation for Power Efficient Data Center Network,'' in {\em Proc. IFIP Networking}, Stockholm, Sweden, Jun. 12-15, 2017 (acceptance rate: 28\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Atilla Eryilmaz, Ness B. Shroff, and Elizabeth S. Bentley, ``Heavy-Ball: A New Approach to Tame Delay and Convergence in Wireless Network Optimization,'' in {\em Proc. IEEE INFOCOM}, San Francisco, CA, Apr. 10-15, 2016 ({\bf Best Paper Award}, acceptance rate: 17\%).

\vspace*{.08in} \item \textbf{Jia Liu}, ``Achieving Low-Delay and Fast-Convergence in Stochastic Network Optimization: A Nesterovian Approach,'' in {\em Proc. ACM SIGMETRICS}, Antibes Juan-les-Pins, France, Jun. 14-18, 2016 (acceptance rate: 13\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Atilla Eryilmaz, Ness B. Shroff, and Elizabeth S. Bentley, ``Understanding the Impact of Limited Channel State Information on Massive MIMO Network Performances,'' in {\em Proc. ACM MobiHoc}, Paderborn, Germany, Jul. 5-8, 2016 (acceptance rate: 17\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Cathy H. Xia, Ness B. Shroff, and Hanif D. Sherali, ``Distributed Optimal Load Shedding for Disaster Recovery in Smart Electric Power Grids: A Second-Order Approach,'' in {\em Proc. ACM SIGMETRICS}, Austin, TX, Jun. 16-20, 2014.

\vspace*{.08in} \item \textbf{Jia Liu}, Cathy H. Xia, Ness B. Shroff, and Hanif D. Sherali, ``Distributed Cross-Layer Optimization in Wireless Networks: A Second-Order Approach,'' in {\em Proc. IEEE INFOCOM 2013}, Turin, Italy, Apr. 14-19, 2013 ({\bf Best Paper Runner-up Award}, acceptance rate: 17\%).

\vspace*{.08in} \item \textbf{Jia Liu} and Hanif D. Sherali, ``A Distributed Newton's Method for Joint Multi-Hop Routing and Flow Control: Theory and Algorithm,'' in {\em Proc. IEEE INFOCOM}, Orlando, FL, Mar. 25 - 30, 2012 (acceptance rate: 18\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Qian Chen, and Hanif D. Sherali, ``Algorithm Design for Femtocell Base Station Placement in Commercial Building Environments,'' in {\em Proc. IEEE INFOCOM}, Orlando, FL, Mar. 25 - 30, 2012  (acceptance rate: 18\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Tianyou Kou, Qian Chen, and Hanif D. Sherali, ``On Wireless Network Infrastructure Optimization for Cyber-Physical Systems in Future Smart Buildings,'' in {\em Proc. IEEE WASA}, Yellow Mountains, China, Aug. 8-10, 2012.


\vspace*{.08in} \item Yi Shi, \textbf{Jia Liu}, Canming Jiang, Cunhao Gao, and Y. Thomas Hou, ``An Optimal Link Layer Model for Multi-hop MIMO Networks,'' in {\em Proc. IEEE INFOCOM 2011}, Shanghai, China, Apr. 10 - 15, 2011 ({\bf Best Paper Runner-up Award}, acceptance rate: 15\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Yi Shi, and Y. Thomas Hou, ``A Tractable and Accurate Cross-Layer Model for Multi-Hop MIMO Ad Hoc Networks,'' in {\em Proc. IEEE INFOCOM 2010}, San Diego, CA, Mar. 15 - 19, 2010 (acceptance rate: 18\%).

\vspace*{.08in} \item S. Sushant, Yi Shi, \textbf{Jia Liu}, Y. Thomas Hou, and Sastry Kompella``Is Network Coding Always Good for Cooperative Communications?'' in {\em Proc. IEEE INFOCOM 2010}, San Diego, CA, Mar. 15 - 19, 2010 (acceptance rate: 18\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, Yi Shi, and Hanif D. Sherali, ``On Performance Optimization for Multi-Carrier MIMO Ad Hoc Networks,'' in {\em Proc. ACM MobiHoc 2009}, New Orleans, LA, May 18 - 21, 2009 (acceptance rate: 18\%).

\vspace*{.08in} \item Yi Shi, Y. Thomas Hou, \textbf{Jia Liu}, and Hanif D. Sherali, ``How to Correctly Use the Protocol Interference Model for Multi-hop Wireless Networks,'' in {\em Proc. ACM MobiHoc 2009}, New Orleans, LA, May 18 - 21, 2009 (acceptance rate: 18\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, and Hanif D. Sherali, ``Optimal Power Allocation for Achieving Perfect Secrecy Capacity in MIMO Wire-Tap Channels,'' in {\em Proc. 43rd Annual Conference on Information Sciences and Systems (CISS) 2009}, Baltimore, MD, Mar. 18 - 20, 2009.

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, and Hanif D. Sherali, ``On the Performance of MIMO-Based Ad Hoc Networks under Imperfect CSI,'' in {\em Proc. IEEE MILCOM 2008}, San Diego, CA, Nov. 17 - 19, 2008 (acceptance rate: 27\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, and Hanif D. Sherali, ``Cross-Layer Optimization for MIMO-Based Mesh Networks with Dirty Paper Coding,'' in {\em Proc. IEEE ICC 2008} ({\bf Best Paper Award}), Beijing, China, May 19 - 23, 2008 (acceptance rate: 27\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou and Hanif D. Sherali, ``Maximum Weighted Sum Rate of Multi-Antenna Broadcast Channels,'' in {\em Proc. IEEE ICC 2008}, Beijing, China, May 19 - 23, 2008 (acceptance rate: 27\%).

\vspace*{.08in} \item \textbf{Jia Liu} and Y. Thomas Hou, ``Weighted Proportional Fairness Capacity of Gaussian MIMO Broadcast Channels,'' in {\em Proc. IEEE INFOCOM 2008}, Phoenix, AZ, Apr. 13 - 17, 2008 (acceptance rate: 20\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, and Hanif D. Sherali, ``Conjugate Gradient
Projection Approach for MIMO Gaussian Broadcast Channels,'' in {\em Proc. IEEE ISIT}, Nice, France,
Jun. 24 - 29, 2007. % (acceptance rate: 50\%).

\vspace*{.08in} \item \textbf{Jia Liu}, T. Y. Park, Y. Thomas Hou, Yi Shi, and Hanif D. Sherali,
``Cross-Layer Optimization of MIMO-Based Mesh Networks Under Orthogonal Channels,'' in {\em Proc.
IEEE WCNC}, Hong Kong, Mar. 11 - 15, 2007. % (acceptance rate: 47\%).

\vspace*{.08in} \item \textbf{Jia Liu}, Y. Thomas Hou, Yi Shi, and Hanif D. Sherali, ``Optimization
of Multiuser MIMO Networks with Interference,'' {\em Proc. IEEE GLOBECOM}, San Franscisco, Nov. 27
- Dec. 1, 2006. % (acceptance rate: 40\%).

\vspace*{.08in} \item \textbf{Jia Liu} and A. Annamalai, ``Efficacy of Channel-and-Node Aware
Routing Strategies in Wireless Ad Hoc Networks,'' in {\em Proc. IEEE VTC}, Dallas, Oct. 2005. % (acceptance rate: 40\%).

\vspace*{.08in} \item \textbf{Jia Liu} and A. Annamalai, ``Channel-Aware routing Protocol for Ad
Hoc Networks: Generalized Multiple-Route Path Selection Diversity,'' in {\em Proc. IEEE VTC},
Dallas, Oct. 2005. % (acceptance rate: 40\%).

\vspace*{.08in} \item A. Annamalai and \textbf{Jia Liu}, ``A Cross-Layer Design Perspective for
Multi-Resolution Signaling,'' in {\em Proc. IEEE GLOBECOM}, Dallas, Nov. 2004. % (acceptance rate: 38\%). 

\vspace*{.08in} \item \textbf{Jia Liu} and A. Annamalai, ``Multi-Resolution Signaling for
Multimedia Multicasting,'' in {\em Proc. IEEE VTC}, Los Angeles, Sep. 2004. % (acceptance rate: 50\%).

\end{enumerate}


%%------------------------------------------------------------------------------

\section{\bf \large Affliations/Memberships}
\vspace{.1in} IEEE Senior Member

\vspace{-.1in} ACM Member

\vspace{-.1in} Member of Society for Industrial and Applied Mathematics (SIAM) (since 2007)

\vspace{-.1in} Member of Tau Beta Pi, the National Engineering Honor Society (since 2006)

\vspace{-.1in} Member of Eta Kappa Nu (HKN), Electrical and Computer Honor Society (since 2008)

\section{\bf \large Professional Services}
\vspace{.16in}
\hspace{-.55in} {\bf Reviewer for Journals}
\vspace{.16in}
\begin{itemize}
\item IEEE/ACM Transactions on Networking (2013, 2014, 2015, 2016)
\item IEEE Transactions on Information Theory (2009)
\item IEEE Transactions on Mobile Computing (2009, 2010)
\item IEEE Transactions on Wireless Communications (2004, 2005, 2006, 2007, 2008, 2009, 2010)
\item IEEE Transactions on Vehicular Technologies (2004, 2005, 2006, 2007, 2012)
\item IEEE Journal on Selected Areas in Communications (2010, 2011, 2012)
\item EURASIP Journal on Advances in Signal Processing (2008)
\end{itemize}

\hspace{-.55in} {\bf Reviewer for Conferences}
\vspace{.16in}
\begin{itemize}
\item IEEE INFOCOM (2007--2020)
\item ACM MobiHoc (2016-2020)
\item ACM SIGMETRICS (2016-2018)
\item IEEE ICC (2007, 2008, 2009, 2010)
\item IEEE GLOBECOM (2004, 2009)
\item IEEE WCNC (2005, 2007)
\item IEEE SECON (2005)
\item VTC (2004, 2005)
\end{itemize}


\hspace{-.55in} {\bf Technical Program Committee (TPC) Member}
\vspace{.16in}
\begin{itemize}
\item IEEE INFOCOM (2010--2020)
\item ACM MobiHoc (2017--2020)
\item IEEE ICCCN (2013)
\item IEEE WCNC (2013, 2014)
\item IEEE WASA (2011--2012)
\item IEEE CNS (2013)
\end{itemize}

\hspace{-.55in} {\bf Submission and Publication Chair}
\vspace{.16in}
\begin{itemize}
\item ACM MobiHoc 2020
\end{itemize}

\hspace{-.55in} {\bf NSF Panelist}
\vspace{.16in}
\begin{itemize}
\item NeTS (2017)
\item CSR (2018)
\item NeTS (2019)
\end{itemize}

\hspace{-.55in} {\bf University Services}
\vspace{.16in}
\begin{itemize}
\item Department Graduate Committee (Fall 2017 --  Present)
\item Department Equipment Committee (Fall 2017 --  Present)
\item Registration Chair,  2019 Midwest Big Data Summer School, at Iowa State University
\item Faculty Search Committee Member, Fall 2019, Department of Statistics, Iowa State University
\end{itemize}


\section{\bf \large Mentoring Experiences}
\vspace{.16in}
\hspace{-.55in} {\bf Ph.D. Students}
\vspace{.16in}
\begin{itemize}
\item Wenbo Ren: 08/2016 -- Present (Co-advised with Prof. Ness B. Shroff 
in CSE at The Ohio State University); Research Areas: Preference learning under incomplete information; Network optimization

\item Xin Zhang: 01/2018 -- Present (Co-advised with Prof. Zhengyuan Zhu 
in Statistics at Iowa State University); Research Areas: Machine learning theory; data analytics

\item Minghong Fang: 09/2017 -- Present; Research Areas: Recommendation systems security; Deep learning

\item Ye Tian: 08/2018 -- Present; Research Areas: Crowdsourcing; Sharing economy

\item Zhengxiong Yuan: 08/2018 -- Present; Research Areas: Scheduling; Network optimization; Machine learning system design

\item Haibo Yang: 08/2018 -- Present; Research Areas: Optimization theory; 
Control theory; Algorithm design

\item Menglu Yu: 08/2018 -- Present; Research Areas: Machine learning system design; Scheduling; Network optimization

\item Zhuqing Liu: 09/2019 -- Present; Research Areas: Optimization for Machine Learning
\end{itemize}

\hspace{-.55in} {\bf M.S. Students}
\vspace{.16in}
\begin{itemize}
\item Hamad Ullah: 01/2020 -- Present; Research Areas: Wireless network systems simulation and performance evaluation

\item Cheng Xiang: 08/2019 -- Present; Research Areas: Wireless network systems simulation and performance evaluation

\item Zehua Li: 09/2017 -- 07/2019; Research Areas: Wireless network systems simulation and performance evaluation

\item Tianchen Zhou: 08/2018 --  Present; Research Areas: Reinforcement learning; Multi-armed bandits

\item Baoyue Bi: 09/2017 -- 12/2017; Research Areas: Wireless network optimization
\end{itemize}

\hspace{-.55in} {\bf Undergraduate Students}
\vspace{.16in}
\begin{itemize}
\item John Wahlig: 09/2018 -- Present; Research Areas: Wireless network optimization ({\bf recipient of the 2020 Dean's High Impact Award for Undergraduate Research from College of Liberal Art and Sciences.})
\end{itemize}

\hspace{-.55in} {\bf Postdoctoral Researchers}
\vspace{.16in}
\begin{itemize}
%\item Hejain Sang: 05/2018 -- Present; Research Areas: Non-convex optimization, Machine learning theory

\item Zhida Qin: Expected to start in 05/2020; Research Areas: Crowd-sensing
\end{itemize}


%\hspace{-.55in} {\bf Visiting Scholars}
%\vspace{.16in}
%\begin{itemize}
%\item Wenchao Li, 11/16-11/17, (Assoc. Professor, University of Electronic Science and Technology of China); Research Areas: Signal processing
%\end{itemize}


%------------------------------------------------------------------------------

%\section{\bf \large Related Courses}
%\vspace{.1in}
%\begin{tabular}{@{}p{.75in}p{3.5in}p{2in}}
%BC 5984 & Principles Construction I & A \\
%BC 5984 & Principles Construction II & A- \\
%BC 5984 & Construction Practice I & A \\
%BC 4444 & Construction Practice II & A \\
%BC 5244 & Preservation: Practices & A \\
%BC 5264 & Fundamentals Indoor Air Science & A \\
%BC 5984 & Sustainable Building Construction & A \\
%ARCH 5045 & Environmental Design Research & A \\
%CE 5602 & Project Management \& Site Control & A \\
%CE 5603 & Engineering Economy \& Project Evaluation & B+ \\
%BC 6064 & Past, Present, Future AEC & A \\
%EDP 6005 & Seminar Environmental Planning - Research & A \\
%EDP 6006 & Seminar Environmental Planning - Teaching & A- \\
%\end{tabular}

%\newpage
%\medskip
%\section{\bf \large References}
%%{\small
%\vspace{.1in}
%{\bf Dr. Ness B. Shroff} \\
%Chaired Professor of ECE and CSE, IEEE Fellow \\
%Ohio Eminent Scholar in Networking and Communications \\
%Department of Electrical and Computer Engineering \\
%The Ohio State University \\
%764 Dreese Laboratory, Columbus, OH 43210\\
%Tel: (614) 247-6554 \\
%Email: shroff.11@osu.edu\\
%({\em PostDoc Advisor}) 
%
%
%\medskip
%{\bf Dr. Y. Thomas Hou}                  \\
%Bradley Distinguished Professor of ECE, IEEE Fellow \\
%Department of Electrical and Computer Engineering \\
%Virginia Polytechnic Institute and State University    \\
%2040-M Torgersen Hall, Blacksburg, VA 24061  \\
%Tel: (540) 231-2950 \\
%Email: thou@vt.edu \\
%({\em Ph.D. Advisor})
%%
%%
%%\medskip
%%{\bf Dr. Atilla Eryilmaz} \\ %(Ph.D. Committee Member) \\
%%Associate Professor  \\
%%Department of Electrical and Computer Engineering \\
%%The Ohio State University \\
%%760 Dreese Laboratory, Columbus, OH 43210 \\
%%Tel: (614) 292-7464 \\
%%Email: eryilmaz.2@osu.edu
%%
%%
%
%\medskip
%{\bf Dr. Hanif D. Sherali} \\ %(Ph.D. Committee Member, Coauthor of ?? Papers) \\
%University Distinguished Professor \\
%W. Thomas Rice Endowed Chaired Professor of Engineering\\
%Elected Member, U.S. National Academy of Engineering, INFORMS Fellow \\
%Department of Industrial and Systems Engineering \\
%Virginia Polytechnic Institute and State University \\
%547 Whittemore Hall, Blacksburg, VA 24061 \\
%Tel: (540) 231-5474\\
%Email: hanifs@vt.edu
%
%%
%%%\medskip
%%%{\bf Dr. Jeffrey H. Reed} \\ %(Ph.D. Committee Member) \\
%%%W. Worcester Endowed Professor, IEEE Fellow  \\
%%%Department of Electrical and Computer Engineering \\
%%%Virginia Polytechnic Institute and State University \\
%%%439 Durham Hall, Blacksburg, VA 24061 \\
%%%Tel: (540) 231-2972 \\
%%%Email: reedjh@vt.edu
%%
%
%\medskip
%{\bf Dr. John L. Volakis} \\ %(Ph.D. Committee Member) \\
%Dean at the College of Engineering and Computing, IEEE Fellow  \\
%Professor, Department of Electrical and Computer Engineering \\
%Florida International University \\
%10555 W. Flagler Street Miami, FL 33174 \\
%Tel: 305-348-1197 \\
%Email: jvolakis@fiu.edu
%
%
%
%%\medskip
%%{\bf Dr. Cathy H. Xia} \\ % (Ph.D. Committee Member) \\
%%Associate Professor                          \\
%%Department of Integrated Systems Engineering \& \\
%%(by courtesy) Department of Computer Science and Engineering \\
%%The Ohio State University \\
%%242 Baker Systems Engineering, Columbus, OH 43210 \\
%%Tel: (614) 249-6985 \\
%%Email: xia.52@osu.edu
%%



\end{resume}
\end{document}

%%===========================================================================%%
